Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-18 edubots_surveys.Rnw
Adds contributions.
If you don't agree with it, just change them. @aguillen @fbarrango @amorag @pacastillo @oliatsi @noorhanabbas

PAC has...
AMM has ...
FB has...
NA has...
OT has...
AG has...

@@

% Antonio - here we can explain what we have done author briefly.

>>>>

PAC has revised the paper and researched the state of the art, as well as contributed to the survey design.
AMM has revised the paper and researched the state of the art, as well as contributed to the survey design.
FB has made the analysis and processed data and contributed to the survey design.
NA has supervised the state of the art, and written the bulk of it, as well as contributed to discussion and conclusions.
OT has performed data analysis, and contributed to discussion and conclusions.
AG has contributed to the design of the survey, analysis, discussion and conclusions.

@@
